Evolution of pre-copulatory and post-copulatory inbreeding behaviour and associated polyandry

### 2016-11-01 ms_pre_post.Rmd
Edit up to Discussion

<!--- Co-author wants to talk about polyandry and stuff: But these figures don’t look very symmetrical – there’s stuff going on in Fig 3 that isn’t really noted in the text – should we do a bit more with this? The most obvious difference is that polyandry evolves in B but not D - i.e. when pre-cop IA is costly but not when post-cop IA is costly. Wouldn’t it be helpful to point this out and explain it? NB, presumably polyandry is cost-free in all these simulations? Might it be worth re-iterating that too? --->

@@

When pre-copulatory inbreeding strategy was initialised for random mating, but polyandry and post-copulatory inbreeding strategy allele values were fixed for adaptive inbreeding avoidance (Figure 4A,B), negative pre-copulatory inbreeding allele values became increasingly more frequent ($M_{a}<0$), causing inbreeding avoidance in mate choice. However, $M_{a}$ values were not as negative after $40000$ generations when post-copulatory inbreeding avoidance and polyandry were fixed as they were when no post-copulatory inbreeding avoidance occurred (e.g., compare Figure 4A with Figure 1A, and Figure 4B with Figure 2A). When post-copulatory inbreeding strategy was initialised for random fertilisation, existence of an already adaptive strategy of pre-copulatory inbreeding avoidance precluded evolution of polyandry and post-copulatory inbreeding avoidance (Figure 4C,D). Mean allele values affecting polyandry consistently decreased over generations regardless of the cost of post-copulatory inbreeding strategy, $c_{F}$. Consequently, when $c_{F}=0$, post-copulatory inbreeding strategy allele values had no effect because females were consistently monandrous, resulting in high drift of $F_{a}$ values among replicates (Figure 4C). However, when $c_{F}=0.02$, $F_{a}$ values remained near zero to minimise direct costs. This lack of evolution of post-copulatory inbreeding avoidance was driven by a lack of polyandry, and therefore an inability of females to bias fertilisation among multiple mates. When pre-copulatory inbreeding avoidance and polyandry were both fixed ($M_{a}=-10$ and $P_{a}=1$), post-copulatory inbreeding strategy evolved to similarly negative mean allele values as pre-copulatory inbreeding strategy did in Figure 4A,B (see Supporting Information).

>>>>

<!--- Co-author wants to talk about polyandry and stuff: ''But these figures don’t look very symmetrical – there’s stuff going on in Fig 3 that isn't really noted in the text – should we do a bit more with this? The most obvious difference is that polyandry evolves in B but not D - i.e. when pre-cop IA is costly but not when post-cop IA is costly. Wouldn’t it be helpful to point this out and explain it? NB, presumably polyandry is cost-free in all these simulations? Might it be worth re-iterating that too?'' --->

@@

When polyandry and post-copulatory inbreeding strategy allele values were fixed for adaptive inbreeding avoidance, pre-copulatory inbreeding avoidance evolved (i.e., $M_{a}$ values became increasingly negative; Figure 4A). Such evolution still occurred, but to a much smaller degree, when pre-copulatory inbreeding avoidance was costly (Figure 4B). However, after $40000$ generations, $M_{a}$ values were less negative when post-copulatory inbreeding avoidance and polyandry were fixed at non-zero values than when they also evolved from initial values of zero (e.g., compare the blue lines in Figures 4A versus Figure 1A).

When pre-copulatory inbreeding strategy values were fixed for adaptive inbreeding avoidance, mean $F_{a}$ allele values did not consistently trend toward negative values (Figure 4C,D). Additionally, mean $P_{a}$ allele values consistently decreased over generations regardless of the cost of post-copulatory inbreeding strategy (Figure 4C,D). Consequently, when $c_{F}=0$, $F_{a}$ allele values had no effect because females were almost exclusively monandrous, resulting in high drift of $F_{a}$ values among replicates (illustrated by wide standard errors, Figure 4C). However, when $c_{F}=0.02$, $F_{a}$ values remained near zero to minimise direct costs. This lack of evolution of post-copulatory inbreeding avoidance was driven by a lack of polyandry, and therefore an inability of females to bias fertilisation among multiple mates. When pre-copulatory inbreeding avoidance and polyandry were both fixed ($M_{a}=-10$ and $P_{a}=1$), $F_{a}$ allele values evolved to similarly negative means as $M_{a}$ allele values in Figure 4A,B (see Supporting Information).
